Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the `eechidna` `R` package.

### 2019-03-29 04-results.Rmd
updated gridvisreg

# Grid visreg
grid_visreg <- function(varname, xvar_title = "", xlimits = NULL, ylimits = NULL, plot = FALSE, table = TRUE, years = FALSE) {
  if (plot == TRUE) {

    if (years == TRUE) {
    p16 <- my_visreg(glsmod16, sp_weights_16, varname = varname, plot = T, nolabs = T, 
      year = "2016", xlimits, ylimits)
    p13 <- my_visreg(glsmod13, sp_weights_13, varname = varname, plot = T, nolabs = T, 
      year = "2013", xlimits, ylimits)
    p10 <- my_visreg(glsmod10, sp_weights_10, varname = varname, plot = T, nolabs = T, 
      year = "2010", xlimits, ylimits)
    p07 <- my_visreg(glsmod07, sp_weights_07, varname = varname, plot = T, nolabs = T, 
      year = "2007", xlimits, ylimits)
    p04 <- my_visreg(glsmod04, sp_weights_04, varname = varname, plot = T, nolabs = T, 
      year = "2004", xlimits, ylimits)
    p01 <- my_visreg(glsmod01, sp_weights_01, varname = varname, plot = T, nolabs = T, 
      year = "2001", xlimits, ylimits)
    } else {
      p16 <- my_visreg(glsmod16, sp_weights_16, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    p13 <- my_visreg(glsmod13, sp_weights_13, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    p10 <- my_visreg(glsmod10, sp_weights_10, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    p07 <- my_visreg(glsmod07, sp_weights_07, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    p04 <- my_visreg(glsmod04, sp_weights_04, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    p01 <- my_visreg(glsmod01, sp_weights_01, varname = varname, plot = T, nolabs = T, 
      xlimits, ylimits)
    }

    if (table == TRUE) {
      plots <- grid.arrange(p01, p04, p07, p10, p13, p16, nrow = 1, 
        bottom = grid.text(xvar_title, gp = gpar(fontface = "bold", cex = 0.6)))
    } else {
      plots <- grid.arrange(p01, p04, p07, p10, p13, p16, nrow = 1, 
        left = grid.text("Two-party preferred vote (%)", gp = gpar(cex = 0.8), rot = 90), 
        bottom = grid.text(xvar_title, gp = gpar(cex = 0.8)))
    }

  return(plots)
  }

  if (plot == FALSE) {
    p16 <- my_visreg(glsmod16, sp_weights_16, varname = varname, plot = F, year = "2016")
    p13 <- my_visreg(glsmod13, sp_weights_13, varname = varname, plot = F, year = "2013")
    p10 <- my_visreg(glsmod10, sp_weights_10, varname = varname, plot = F, year = "2010")
    p07 <- my_visreg(glsmod07, sp_weights_07, varname = varname, plot = F, year = "2007")
    p04 <- my_visreg(glsmod04, sp_weights_04, varname = varname, plot = F, year = "2004")
    p01 <- my_visreg(glsmod01, sp_weights_01, varname = varname, plot = F, year = "2001")

    bands_df <- bind_rows(
      p16$bands %>% mutate(year = "2016"),
      p13$bands %>% mutate(year = "2013"),
      p10$bands %>% mutate(year = "2010"),
      p07$bands %>% mutate(year = "2007"),
      p04$bands %>% mutate(year = "2004"),
      p01$bands %>% mutate(year = "2001")
    )

    points_df <- bind_rows(
      p16$points %>% mutate(year = "2016"),
      p13$points %>% mutate(year = "2013"),
      p10$points %>% mutate(year = "2010"),
      p07$points %>% mutate(year = "2007"),
      p04$points %>% mutate(year = "2004"),
      p01$points %>% mutate(year = "2001")
    )

    return_df <- list(bands = bands_df, points = points_df)

    return(return_df)
  }

@@

@@

@@

### Household mobility
```{r plotdiffaddress, fig.cap = "Effect of DiffAddress", out.width="60%"}
p <- grid_visreg("DiffAddress", xvar_title = "DiffAddress", xlimits = c(-2.1, 3.65), ylimits = c(34, 81), plot = T)
```

In each of the six elections, electorates with a higher proportion of people that have recently moved house (meaning in last five years) were more likely to support the Liberal party, although this effect was marginally insignificant in 2013. Having controlled for characteristics of house ownership and rental prices (via the factors `PropertyOwned` and `RentLoan` respectively), this is effect is somewhat surprising.

@@

*Move the individual plots in each section to a global grid here*

@@

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[8:13])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[8:13]), size = 0.75, col = "grey50") + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw()+ 
  labs(x = varname, y = "Response") + 
  facet_wrap(varname ~ year, ncol = 6, scales = "free")

my_x_ranges <- range(range(model_df$Judaism), range(model_df$Born_Asia), range(model_df$Born_SE_Europe), range(model_df$OtherLanguageHome), range(model_df$Education), range(model_df$MedianAge), range(model_df$DeFacto), range(model_df$DiffAddress), range(model_df$ManagerAdminClericalSales), range(model_df$Transformative), range(model_df$Extractive), range(model_df$Unemployment), range(model_df$Incomes))

my_y_ranges <- range(
  range(c(ls_visreg$Judaism$bands$upper95, ls_visreg$Judaism$bands$lower95, ls_visreg$Judaism$points$part_res)),
  range(c(ls_visreg$Born_Asia$bands$upper95, ls_visreg$Born_Asia$bands$lower95, ls_visreg$Born_Asia$points$part_res)),
  range(c(ls_visreg$Born_SE_Europe$bands$upper95, ls_visreg$Born_SE_Europe$bands$lower95, ls_visreg$Born_SE_Europe$points$part_res)),
  range(c(ls_visreg$OtherLanguageHome$bands$upper95, ls_visreg$OtherLanguageHome$bands$lower95, ls_visreg$OtherLanguageHome$points$part_res)),
  range(c(ls_visreg$Education$bands$upper95, ls_visreg$Education$bands$lower95, ls_visreg$Education$points$part_res)),
  range(c(ls_visreg$MedianAge$bands$upper95, ls_visreg$MedianAge$bands$lower95, ls_visreg$MedianAge$points$part_res)),
  range(c(ls_visreg$DeFacto$bands$upper95, ls_visreg$DeFacto$bands$lower95, ls_visreg$DeFacto$points$part_res)),
  range(c(ls_visreg$DiffAddress$bands$upper95, ls_visreg$DiffAddress$bands$lower95, ls_visreg$DiffAddress$points$part_res)),
  range(c(ls_visreg$ManagerAdminClericalSales$bands$upper95, ls_visreg$ManagerAdminClericalSales$bands$lower95, ls_visreg$ManagerAdminClericalSales$points$part_res)),
  range(c(ls_visreg$Transformative$bands$upper95, ls_visreg$Transformative$bands$lower95, ls_visreg$Transformative$points$part_res)),
  range(c(ls_visreg$Extractive$bands$upper95, ls_visreg$Extractive$bands$lower95, ls_visreg$Extractive$points$part_res)),
  range(c(ls_visreg$Unemployment$bands$upper95, ls_visreg$Unemployment$bands$lower95, ls_visreg$Unemployment$points$part_res)),
  range(c(ls_visreg$Incomes$bands$upper95, ls_visreg$Incomes$bands$lower95, ls_visreg$Incomes$points$part_res))
  )

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[13])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[13]), size = 0.75, col = "grey50") + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw() + 
  labs(x = varname, y = "Response") + 
  facet_wrap(varname ~ year, ncol = 6, scales = "free") +
  expand_limits(x = c(-2, 2))
  expand_limits(x = my_x_ranges[25:26], y = my_y_ranges[25:26])

@@

```{r}
cooksd_df %>% 
  filter(cooksd > 0.1) %>% 
  select(DivisionNm, StateAb, year, cooksd, Residuals, LNP_Percent, everything()) %>% View
```

>>>>

# Grid visreg
grid_visreg <- function(varname, plot = TRUE, myscale = "free") {

    p16 <- my_visreg(glsmod16, sp_weights_16, varname = varname, plot = F, year = "2016")
    p13 <- my_visreg(glsmod13, sp_weights_13, varname = varname, plot = F, year = "2013")
    p10 <- my_visreg(glsmod10, sp_weights_10, varname = varname, plot = F, year = "2010")
    p07 <- my_visreg(glsmod07, sp_weights_07, varname = varname, plot = F, year = "2007")
    p04 <- my_visreg(glsmod04, sp_weights_04, varname = varname, plot = F, year = "2004")
    p01 <- my_visreg(glsmod01, sp_weights_01, varname = varname, plot = F, year = "2001")

    bands_df <- bind_rows(
      p16$bands %>% mutate(year = "2016"),
      p13$bands %>% mutate(year = "2013"),
      p10$bands %>% mutate(year = "2010"),
      p07$bands %>% mutate(year = "2007"),
      p04$bands %>% mutate(year = "2004"),
      p01$bands %>% mutate(year = "2001")
    ) %>% mutate(varname = varname)

    points_df <- bind_rows(
      p16$points %>% mutate(year = "2016"),
      p13$points %>% mutate(year = "2013"),
      p10$points %>% mutate(year = "2010"),
      p07$points %>% mutate(year = "2007"),
      p04$points %>% mutate(year = "2004"),
      p01$points %>% mutate(year = "2001")
    ) %>% mutate(varname = varname)

    if (plot == T) {
      return_object <- ggplot(data = bands_df) +
        geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
        geom_point(aes(x = variable, y = part_res), data = points_df, size = 0.5, shape = 1, alpha = 0.5) +
        geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
        theme_bw() + 
        labs(x = "", y = "") + 
        facet_grid(varname ~ year, scales = "free") + 
        theme(strip.text.x = element_blank())

      if (myscale == "free") {
        return_object <- return_object + lims(x = range(model_df %>% select(varname)), 
          y = range(c(bands_df$upper95, bands_df$lower95, points_df$part_res)))
      }

      if (myscale == "free_x") {
        return_object <- return_object + lims(x = range(model_df %>% select(varname)))
      }

      if (myscale == "free_y") {
        return_object <- return_object + lims(y = range(c(bands_df$upper95, bands_df$lower95, points_df$part_res)))
      }

      if (myscale == "none") {
        return_object <- return_object
      }
    }

    if (plot == F) {
      return_object <- list(bands = bands_df, points = points_df)
    }

    return(return_object)

@@

```{r}
grid_visreg(varname = "Incomes", plot = T)
```

@@

### Household mobility
In each of the six elections, electorates with a higher proportion of people that have recently moved house (meaning in last five years) were more likely to support the Liberal party, although this effect was marginally insignificant in 2013. Having controlled for characteristics of house ownership and rental prices (via the factors `PropertyOwned` and `RentLoan` respectively), this is effect is somewhat surprising.

#### Individual*

@@

```{r plotdiffaddress, fig.cap = "Effect of DiffAddress", out.width="60%"}
p <- grid_visreg("DiffAddress", xvar_title = "DiffAddress", xlimits = c(-2.1, 3.65), ylimits = c(34, 81), plot = T)
```

@@

#### *Move the individual plots in each section to a global grid here*

@@

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[1:6])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[1:6]), size = 0.5, shape = 1, alpha = 0.5) + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw()+ 
  labs(x = "", y = "Two-party preferred vote (%)") + 
  facet_grid(varname ~ year, scales = "free_x") + theme(strip.text.x = element_blank())

my_x_ranges <- c(range(model_df$Judaism), range(model_df$Born_Asia), range(model_df$Born_SE_Europe), range(model_df$OtherLanguageHome), range(model_df$Education), range(model_df$MedianAge), range(model_df$DeFacto), range(model_df$DiffAddress), range(model_df$ManagerAdminClericalSales), range(model_df$Transformative), range(model_df$Extractive), range(model_df$Unemployment), range(model_df$Incomes))

my_y_ranges <- c(
  range(c(ls_visreg$Judaism$bands$upper95, ls_visreg$Judaism$bands$lower95, ls_visreg$Judaism$points$part_res)),
  range(c(ls_visreg$Born_Asia$bands$upper95, ls_visreg$Born_Asia$bands$lower95, ls_visreg$Born_Asia$points$part_res)),
  range(c(ls_visreg$Born_SE_Europe$bands$upper95, ls_visreg$Born_SE_Europe$bands$lower95, ls_visreg$Born_SE_Europe$points$part_res)),
  range(c(ls_visreg$OtherLanguageHome$bands$upper95, ls_visreg$OtherLanguageHome$bands$lower95, ls_visreg$OtherLanguageHome$points$part_res)),
  range(c(ls_visreg$Education$bands$upper95, ls_visreg$Education$bands$lower95, ls_visreg$Education$points$part_res)),
  range(c(ls_visreg$MedianAge$bands$upper95, ls_visreg$MedianAge$bands$lower95, ls_visreg$MedianAge$points$part_res)),
  range(c(ls_visreg$DeFacto$bands$upper95, ls_visreg$DeFacto$bands$lower95, ls_visreg$DeFacto$points$part_res)),
  range(c(ls_visreg$DiffAddress$bands$upper95, ls_visreg$DiffAddress$bands$lower95, ls_visreg$DiffAddress$points$part_res)),
  range(c(ls_visreg$ManagerAdminClericalSales$bands$upper95, ls_visreg$ManagerAdminClericalSales$bands$lower95, ls_visreg$ManagerAdminClericalSales$points$part_res)),
  range(c(ls_visreg$Transformative$bands$upper95, ls_visreg$Transformative$bands$lower95, ls_visreg$Transformative$points$part_res)),
  range(c(ls_visreg$Extractive$bands$upper95, ls_visreg$Extractive$bands$lower95, ls_visreg$Extractive$points$part_res)),
  range(c(ls_visreg$Unemployment$bands$upper95, ls_visreg$Unemployment$bands$lower95, ls_visreg$Unemployment$points$part_res)),
  range(c(ls_visreg$Incomes$bands$upper95, ls_visreg$Incomes$bands$lower95, ls_visreg$Incomes$points$part_res))
  )

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[1])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[1]), size = 0.5, shape = 1, alpha = 0.5) + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw()+ 
  labs(x = "", y = "") + 
  facet_grid(varname ~ year, scales = "free") + theme(strip.text.x = element_blank()) +
  expand_limits(x = my_x_ranges[1:2], y = my_y_ranges[1:2])

, y = my_y_ranges[1:12])
"Two-party preferred vote (%)"

@@

```{r, eval = F}
cooksd_df %>% 
  filter(cooksd > 0.1) %>% 
  select(DivisionNm, StateAb, year, cooksd, Residuals, LNP_Percent, everything()) %>% View
```
